\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Assignment 28}
\author{Xiaoting Li (xil139) \\
Ziyu Zhang (ziz41) \\
Deniz Unal (des204)}
\date{March 2019}

\begin{document}

\maketitle

\noindent
\textbf{49. Problem 35.2-3 from the CLRS text.} \\ \newline
Answer: From the problem, we learn that at each step, we need to  identify the vertex u that is not on the cycle but whose distance to any vertex on the cycle is minimum. This is similar to finding minimum spanning tree using Prim's Algorithm. In order to prove that this heuristic returns a tour whose total cost is not more than twice the cost of an optimal tour, we set the lower bound as minimum spanning tree. And we need to prove $A(I) \leq 2\cdot LB(I) = 2\cdot MST(I)$. Assume that we have $i$ vertices of current cycle. The cost of the algorithm is $C_{i}$. And assume we have $C_{i} \leq 2 \cdot MST_{i}$, $MST_{i}$ is the cost of minimum spanning tree when there are $i$ vertices. We need to show that for $i+1$, we also have $C_{i+1} \leq 2 \cdot MST_{i+1}$. Let's say for $i+1$, the nearest vertex to $v$ is $u$, $w(v, u)$ is the min weight edge. Using Prim's algorithm, we learn that $MST_{i+1} = MST_{i} + w(v, u)$. Assume the vertex after $v$ is $w$. In order to insert $v$ using the heuristic algorithm, we need to remove $w(v, w)$ and add $w(v, u)$ and $w(u, w)$. So we have $C_{i+1} = C{i} - w(v,w) + w(v, u) + w(u, w)$. Based on triangle inequality, we have $w(v, u) + w(v, w) > w(u, w)$. So we have $C_{i+1} \leq C_{i} + 2\cdot w(v,u) \leq 2\cdot MST_{i} + 2\cdot w(v,u) = 2\cdot MST_{i+1}$. So we can conclude that this heuristic returns a tour whose total cost is not more than twice the cost of an optimal tour.\\ \newline
\textbf{50. Problem 35.2-4 from the CLRS text.}\\ \newline
Answer: As our lower bound, we first compute a bottle neck spanning tree in polynomial time. Then we walk around this bottle neck spanning tree to get a hamiltonian cycle $H$. Since we can travel to a node only once in a hamiltonian cycle, we walk around the bottle neck spanning tree using a short cut, as stated in the hint given in the problem (taking a full walk of the tree and skipping nodes, but without skipping more than two consecutive intermediate nodes). If we skip 2 vertices to add an edge to $H$, by triangle inequality the cost of that edge is smaller than the 3 edges that covering the 2 vertices we skipped. If we call the maximum cost edge in the bottle neck spanning tree $M$, then any edge we add to $H$ should be less than or equal to $3M$. If we call the most costly edge in $H$ $M_H$, then from the previous statement we also know that $M_H \leq 3M$. Let us call the cost of the most costly edge in an \textit{optimal} bottleneck hamiltonian cycle $M_{H_{OPT}}$.  We can always get a spanning tree from the optimal hamiltonian cycle by removing the most costly edge in it, and so the minimum cost of the max cost edge in any spanning tree (including the bottle neck spanning tree) is less than or equal to the cost of the most costly edge in any Hamiltonian cycle. So from that we get $M \leq M_{H_{OPT}}$. And this implies $M_H \leq 3 M_{H_{OPT}}$. By this inequality, we can say that there exists a 3 approximation algorithm for solving the bottle neck traveling salesman problem. \\ \newline
\textbf{51.(a) Problem 35.1-5 from the CLRS text} \\ \newline
Answer:  Let $G$ be a graph with $n$ vertices. If the minimum vertex cover is of size $k$ then the size of the largest clique would be $n - k$. Assume we found another vertex cover of size $2k$. Then the complement of $G$ has a vertex cover of size $n - 2k$. In order for this relationship to imply there is a polynomial-time approximation algorithm with a constant approximation ratio for the clique problem, the inequality $n - 2k \geq c(n - k)$ should be correct for some constant $c$. We can show that for some very small $k$ this inequality will not hold, so the relationship between the vertex cover problem and the clique problem does not imply that there is a polynomial-time approximation algorithm with a constant approximation ratio for the clique problem. \\ \newline
\textbf{(b) Problem 35.2-2 from the CLRS text} \\ \newline
Answer: To convert this problem to another instance whose cost function satisfies the triangle inequality, we find the maximum edge cost $m$ among all pairs of cities and add $m$ to each pair of edge cost. Assume that we have edge cost $a, b, c$ for three cities. Since $m$ is the maximum edge cost among all pairs of cities, we have $a + m \leq a + m + b + c \leq (b + m) + (c + m)$, which satisfies triangle inequality. Next, we need prove that the new instance has the same set of optimal tours as TSP. Let's assume the optimal cost of TSP is $c$ and the optimal cost of the new instance is $c^{'}$. Let's assume we have $n$ cities. $c^{'} = c + mn$.If there exists another set of optimal tours whose cost is $c^{''}$, $c^{''}\leq c^{'}$, then we have $c^{''}\leq c^{'} = c + mn$. Then we have $C^{''} - mn \leq c$, which contradicts to the assumption that $c$ is the optimal cost of TSP. So we prove that the new instance has the same set of optimal tours as TSP. Since for $n$ cities, there are $n^2$ pairs of edges, adding $m$ to each pair has the time complexity $O(n^2)$, which is polynomial.\\ \newline
Let's assume we have the new instance is a $\rho$ approximation algorithm for TSP. Then we have $c^{'} \leq \rho \cdot c_{opt}^{'}$. Since from the proof above, we learn that both the new instance and TSP have the same set of optimal tours, so we have $c = c^{'} - mn \leq \rho \cdot c_{opt}^{'} - mn = \rho \cdot (c_{opt} + mn) - mn = \rho \cdot c_{opt} + (\rho - 1)\cdot mn$. Since $\rho \geq 1$, so we know that $c$ is also influenced by $m$ and $n$. So the new instance is not a polynomial-time $\rho$ approximation algorithm for TSP. So this does not contradict with Theorem 35.3.\\ \newline
\textbf{(c) Prove that if there is a polynomial time approximation algorithm for the maximum clique problem that has approximation ratio 1000 then there is a polynomial time approximation algorithm with approximation ratio 1.000000001. This is actually a slightly easier problem than problem 35-2 part b in the CLRS text, which I suggest that you look at for inspiration. Note that in some sense this can be viewed as a gap reduction.}\\ \newline
Answer: 

\end{document}